Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-14 lloveras_2020.tex
nuevas imag

\subsection{DEMT reconstructions}\label{demt}

@@

\subsection{AWSoM simulations}\label{awsom}

@@

\subsection{Tracing of results along fieldlines}\label{trace}

\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM. This requires covering the following points:
\begin{itemize}
  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
  \item A short paragraph describing the numerical method used to trace field lines. We have a nice version of this in your previous paper.  At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$. 
  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell. At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
  \item Explain then the classification of field lines.
\end{itemize}
}

Aiming determination of the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points. Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise. In the case of closed magnetic lines, they are separated in two ``legs", from the base to the apex.

%\diego{Of these legs, those whose size $L$ are smaller than the average lengths $\langle L \rangle$ are called small, and those with $L > \langle L \rangle$ ar called large.}
\diego{
In the case of closed magnetic field lines, legs {are} further classified as ``small" and ``large" upon their apex height being within or beyond the lenght average of the closed legs, respectively.
}

At this stage, all DEMT and AWSoM products, electron density and mean temperature in particular, can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell is obtained. This allows to analyze how density and temperature, coming from both models, vary with height along each individual field line. This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature. For DEMT results the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of AWSoM the data points used were $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

@@

In the present work we focus on legs with increasing and decreasing temperatures in linear form. In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$} {(with 95\% confidence level)}. In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.

The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. Both fits consider tomographic systematic uncertainty estimated in \citet{lloveras_2017}, i.e. $0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$.

To measure how good the quality of the fit are, a chi-square merit function was used (Section 15.2 \citet{recipes}).%, selecting only legs with 95\% confidence level.

%el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
%El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
%En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
%En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion. Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste. En este caso la hipotesis nula es que los datos provienen de esa distrib, con lo cual el chi deberia dar bajo y descartas los que dan valores altos con un 95$\%$ de seguridad. Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).

{To be selected a leg must meet all following conditions.}

\diego{
\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
\item 
The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
\item 
The coefficient level of both the exponential and linear fit must be grater than \%90.
\end{enumerate}
}

{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}

\diego{
\begin{itemize}
\item Type 0 - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr < -0.5$. 
 %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
\item Type I - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr > 0.5$. 
%This class thoroughly populates the inner of the Streamer belt.
\item Type II - Large legs (coming from closed field) in the latitudes range $[-90\mdeg,-40\mdeg] \cup [+40\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$. 
%This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt. 
\item Type III - Open field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$.
\end{itemize}
}
{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}

\subsection{{Energy input flux}}\label{energia}

\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone. The summary will not include any derivation and will refer to Cecilia's paper. Only the results that are relevant are to be explicited. Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes). At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable. This should be a very short section, as it is a summary of one previous paper alone.}

%correcciones a hacer! DIEGO
%Los términos de la Eq (10) requieren ser explicados. La explicación a conituación no es clara, y de hecho está mal escrita. La Eq. (7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo. Utilizando la condición solenoidal de B se llega a la Eq. (7), dónde... y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM. Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo. Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec. (8). y además el texto puede compactarse, corregirse y reordenarse mucho. Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.

Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature. Previous works have studied this mechanism by observations and modeling, but mostly for active regions. \citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity. Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:

@@

\noindent
where $s$ is the position along each magnetic flux tube and the powers are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.

\noindent\notebyalbert{Trabajé todo lo naranja. Primero decidí que es mejor no numerar $E_c$ sino $F_c$. Eso te quedará claro cuando agregues las ecuaciones (11) y (12) que te indico más abajo y leas el último párrafo naranja de abajo, ahí cierra todo. Además describí que son los $\phi$ en forma correcta. El texto previo estaba muy flojón, entre otras cosas se hablaba de una (inexistente) ``conductive loss function" y de una (incorrectamente denominada) ``area along the loop". Obviamente luego de chequear este texto naranja borrá esta nota azul en particular.}

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} \diego{Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III. (NOTA: Estos numeros estan actualizados,  pensaba en ponerlos solo porque en ningun momento hablamos de la proporcion, solo se muestran los histos de gradT)}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   7&4 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Pl&12\%) &   0&97 &(\Pl&~7\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value. \notebyalbert{Propongo que para todas las cantidades absolutas de la Tabla 1 informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca. Doy dos ejemplos para no dejar dudas. Para $\NCB$ de Type-II: $1.0\,(-21\%)$. Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}\diego{Si aca redondeo, Ncb de type 0 y I toman el mismo valor 1.2, y si no redondeo la temp en type III se ve lindo que sea sub-MK.
}}
\label{tabla_demt}
\end{table}

@@

\diego{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and $\approx 10-25\%$ larger values of the electron temperature.}

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized} by $\phi_c<0$.}

\subsection{Tomography and Models}\label{awsom_res}

@@

@@

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&~9\%) \\
II   & 0&99 &(\Mi&25\%)  &   8&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Mi&~8\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&55 &(\Pl&~1\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value. \albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca. Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$. Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$. Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.} \diego{Hay 6 valores que terminan en 5, con lo cual al redondearlos se pierde bastante informacion, lo dejé así como lo vez por eso. Si aún asi te parece buena idea redondearlo, lo hacemos.}}
\label{tabla_comp}
\end{table}

@@

\section{Discussion}\label{discu}

\noindent\notebyalbert{(by Albert) This section will discuss and summarize some main conclusions, possibly in three groups: a) DEMT analysis alone (including thermodynamical structure, up/down loops, energy considerations, etc.), b) Comparison AWSoM/DEMT (longitude-averaged latitudinal profiles, height-dependence profiles in different magnetic structures, etc), and c) Correlation betweem AWSoM terminal wind speed and DEMT basal density, I will expand on this later this week as this may require help from Michigan).}

\diego{NOTE: Here is a paragraph describing the empirical successes in the reconstruction of both rotations.}

>>>>

\subsection{{DEMT Reconstructions}}\label{demt}

@@

\subsection{{AWSoM Simulations}}\label{awsom}

@@

\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}

%\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM. This requires covering the following points:
%\begin{itemize}
%  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
%  \item A short paragraph describing the numerical method used to trace field lines. We have a nice version of this in your previous paper.  At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$. 
%  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell. At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
%  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
%  \item Explain then the classification of field lines.
%\end{itemize}}

{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.

{For analysis purposes, the geometry of all traced magnetic field lines is classified. They are first classified as open or closed according to their full geometry. Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively. This median value is \diego{${\rm Md}(L)=0.50$} and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively. Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e. their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes. Nota: MHD no tiene source surface! Ahora bien, además informo ${\rm Md}(L)$. Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié). Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números. Es importante.}

At this stage, all DEMT and AWSoM products, electron density and {temperature} in particular, can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell {is obtained. This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}. For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

@@

\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down. Además está corregido.} {Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\notebyalbert{Reordené y corregí mucho el siguiente párrafo. Lo que see lee es correcto en cada detalle y palabra? Está bien explicado todo lo que concierne a chi-suqared? La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$. \diego{hablemos sobre esta frase} We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level. In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis. Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}. \notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco. Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}\diego{si!}
\end{enumerate}

{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:} \notebyalbert{Simplifiqué mucho esto.}

{
\begin{itemize}
\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
\end{itemize}
}

In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

\subsection{{Energy Input Flux}}\label{energia}

%\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone. The summary will not include any derivation and will refer to Cecilia's paper. Only the results that are relevant are to be explicited. Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes). At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable. This should be a very short section, as it is a summary of a single previous paper.}

{The high temperature of the corona requires heating mechanisms to compensate for the the losses. While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}

{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:

@@

\noindent
where $s$ is the position along {the flux tube} and the {power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III. \notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones. Algo no está consistente aquí.}\diego{Statloop 6 alturas noda algo asi como 150k piernas, algunas no se trazan (entre 30 y 40k) lo cual nos deja aprox 110k. SUpongo que te quedaste con ese numero. Pero elimino los cuasi isotermicos, perdemos 30k en el streamer y 10k en CH. Luego hacemos una seleccion qie involucra footpoints y ahi perdemos lo que falta! Es decir, el numero del draft ya es des-raleado.}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   7&1 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&66 &(\Mi&12\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&18\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 5-25\%$} larger values of the electron temperature.}

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$. \vfill}} % NOTA el vfill

\subsection{{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}

@@

To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines. For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}){, considering only data points above heliocentric height $1.055\,\mrsun$. We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.  Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}

@@

{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}. The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT. The following major results can be drawn.}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

@@

\section{{Discussion and Conclusions}}\label{discu}
